Keeping and discarding players

### 2021-02-02 inst/retain.Rmd
bugfix

```{r}
keep_flawed(OT,1:2)
```

Above, function `keep_flawed()` has effectively taken `OT`, set `c=0`,
and then discarded the `c^5` term.  This process, while natural, has
the effect of replacing `(a+c)^-4` with `a^-4`, which has no natural
probabilistic interpretation: we are ignoring `c`'s victories but
nevertheless interpreting joint strength term on the denominator [viz
`a+c`] as a *loss* for `a`.

@@

```{r}
keep_flawed(OT,1)
```

>>>>

```{r}
keep_flawed(OT, c("a","b"))
```

Above, function `keep_flawed()` has effectively taken `OT`, set `c=0`,
and then discarded the `c^5` term.  This process, while natural from a
computing perspective, has the effect of replacing `(a+c)^-4` with
`a^-4`, which has no natural probabilistic interpretation: we are
ignoring `c`'s victories but nevertheless interpreting the joint
strength term on the denominator [viz `a+c`] as a *loss* for `a`.

@@

```{r}
keep_flawed(OT,"a")
```
